---
title: "Advertising Budget Project"
output: word_document
date: "4/16/2022"
---

```{r load up regclass, message=FALSE}
library(regclass)
library(ggplot2)
```

**************
Data source: https://www.kaggle.com/datasets/yasserh/advertising-sales-dataset

**1. Introduction: Description of the data that you selected:**

We first importing CSV and look at the data

```{r read d}
d <- read.csv("data/Advertising Budget and Sales.csv")

head(d,3)
```
Then, we look at the distribution of the variables

```{r}

summary(d)
dim(d)

```


**************

**Data Cleaning: Use R to remove all the missing values in the data set and use the complete data for the further steps.:**

To clean the data. Let's look for for missing values.

```{r}

# creating empty data.frame for missing values
missing_values = data.frame()
# check for missing values
for(i in 1:length(d)) {                      
  missing_values[i,1] = is.null(d[i])
}
rownames(missing_values) <- c(names(d))
colnames(missing_values) = "missing values"

missing_values

```

Therefore, there are no missing values. Data is complete and ready for analysis.

Then, I would like to change the columns names

```{r}

d$X = NULL
names(d)[1] <- "TV.Ad.Budget"
names(d)[2] <- "Radio.Ad.Budget"
names(d)[3] <- "Newspaper.Ad.Budget"
names(d)[4] <- "Sales"
```
**3. Association Analysis:**

We want to predict variable "Sales" and we set it as "y". 
```{r}
names(d)[4] <- "y"
head(d,2 )
```
```{r}
all_correlations(d, interest = "y", sorted  = "magnitude")
```
We can see that variable "TV.Ad.Budget" describe the variable "y" the best. Let's examine association between them.

```{r}
plot(y~TV.Ad.Budget,data=d)
```
We can see that variance is increasing. We can see heteroscedasticity.
Let's try log transformation. 

```{r}
associate(log(y)~TV.Ad.Budget,data=d)
```

The relationships is not linear but monotonic. Therefore, we use Spearman correlation

r 0.8006144
p-value 0 and 0.007 

p-value is less then 0.05
Therefore, log(y)~TV.Ad.Budget relationship statistically significant.

Let's examine other associations.

```{r}
plot(y~Radio.Ad.Budget, data = d)
```

Let's use log transformation again. Since th variance is increasing; we see heteroscedasticity.

```{r}
associate(log10(y)~Radio.Ad.Budget,data=d)
```
The relationship is linear. Let's use Person.

Pearson's r 0.4711507
p-value 0 and 0.007 

p-value is less than 0.05. 
Therefore, log10(y)~Radio.Ad.Budget relationship statistically significant 

```{r}
associate(y~Newspaper.Ad.Budget,data=d)
```
 
The relationship looks like ellipse. Let's use Person.

Pearson's r   0.2282990
p-value 0 and 0.007 

p-value is less than 0.05.
Therefore, y~Newspaper relationship statistically significant 


**4. Simple Linear Regression:**

log(y)~log(TV.Ad.Budget)

Let's use log transformation on both variables to build  simple Linear Regression.
```{r}
l12=lm(log(y)~log(TV.Ad.Budget) , data=d)
summary(l12)
```

```{r}
possible_regressions(l12)
```
The slope of our regression is steep. The SSE reduction is much larger than what happens “by chance”. 
The regression is statistically significant.

```{r}
confint(l12, level =0.05)
```

Let's do the same with log(y) ~ Radio.Ad.Budget+1. We have to add +1 to Radio.Ad.Budget because it has values of "0" what prevent R from creating the linear regression model.
```{r}
l22=lm(log(y) ~ log(Radio.Ad.Budget+1),data=d)
summary(l22)
```

```{r}
possible_regressions(l22)
```
The slope of our regression is steep. The SSE reduction is much larger than what happens “by chance”. 
The regression is statistically significant.


```{r}
confint(l22, level =0.05)
```
Let's compare the selected linear models 

1) log(y)~log(TV.Ad.Budget)
Residual standard error: 0.2109
Multiple R-squared:  0.7421,	Adjusted R-squared:  0.7408 

2) log(y)~TV.Ad.Budget
Residual standard error: 0.2575 
Multiple R-squared:  0.6156,	Adjusted R-squared:  0.6137 

3) log10(y) ~ log(Radio.Ad.Budget+1)
Residual standard error: 0.3687 on 198 degrees of freedom
Multiple R-squared:  0.212,	Adjusted R-squared:  0.208 
F-statistic: 53.28 on 1 and 198 DF,  p-value: 6.866e-12

We also examened y~Newspaper~Ad.Budget relationship. However, the association would not be in the limit of 10 pages. 
4) y~Newspaper.Ad.Budget
Residual standard error: 5.092 
Multiple R-squared:  0.05212,	Adjusted R-squared:  0.04733 

Based on R square, and Residual standard error, the best linear regression that explain variable y (Sales) the best is  log(y)~log(TV.Ad.Budget) (1).


